Measuring contrast processing in the visual system using SSVEP

### 2024-11-27 review.qmd
Finished adaptation

Similar changes to the contrast response function might also be obtained using adaptation paradigms, in which the visual system is exposed to high contrast stimuli for long durations. Psychophysically, adaptation increases detection thresholds, but has little effect on contrast discrimination performance [@Ross1993], much like pattern masks [@Foley1994]. Although SSVEP adaptation effects show strong tuning for orientation [@Vergeer2018; @Campbell1970] and spatial frequency [@Mecacci1976], there appear to be no studies measuring the full SSVEP contrast response function before and after an extended period of adaptation.

>>>>

Similar changes to the contrast response function might also be obtained using adaptation paradigms, in which the visual system is exposed to high contrast stimuli for long durations. Psychophysically, adaptation increases detection thresholds, but has little effect on contrast discrimination performance [@Ross1993], much like pattern masks [@Foley1994]. Although SSVEP adaptation effects show strong tuning for orientation [@Vergeer2018; @Campbell1970] and spatial frequency [@Mecacci1976], there appear to be very measurements of the full SSVEP contrast response function before and after an extended period of adaptation. One exception is a study by Bach et al [@BachGreenleeBuhler1988] that examined the effects of adaptation on SSVEP responses who found a paradoxical increase in the 1F SSVEP amplitude following prolonged exposure to high-contrast stimuli across much of the probe contrast range. They explain this as being due to the presence of a nonlinear transducer function that saturates at high probe contrast driving the response to higher harmonic frequencies. Adaptation reduces the apparent contrast of the input, leading to less distortion, a more sinusoidal output and a concentration of the frequency-tagged response at lower harmonics. This explanation is conceptually related to the 'supersaturation' that we observe in Figure xxx.
